### 2020-05-27 2_task_bench.tex
More tweaks to reduce page count.
Apply Brad Chamberlain's comments.
Update text on validation.

\brokenpenalty=0

@@

\brokenpenalty=\oldbrokenpenalty

@@

Dependencies between tasks are determined by a dependence
relation. The
dependence relation identifies the tasks from the
previous time step each task depends on, permitting a wide variety
of patterns to be implemented that are relevant to real
applications: stencils,
sweeps, FFTs, trees, etc. Dependence relations may be
parameterized, such as picking the $K$ nearest neighbors, or $K$
distant neighbors. They may also vary over time, such as in the FFT pattern. The set of dependence relations is extensible, making it easy to add patterns to represent new classes applications. Table~\ref{tab:equations} shows equations for the
dependence relations of the patterns in Figure~\ref{fig:task-graphs},
where $t$ is timestep, $i$ is column, and $W$ is the width of the task
graph.

@@

The Task Bench core library is fully
validating. Because the task graph configuration is explicitly
represented (though unmaterialized) in Task Bench, this representation
can be queried to determine exactly what dependencies a task should
expect. The output of every task in Task Bench is unique,
and all inputs are verified. An assertion is thrown if validation
fails. These checks ensure that every execution of Task Bench, if it
completes successfully, is correct. An evaluation of the performance impact of
validation showed it to be less than 3\% at the smallest task
granularities in any Task Bench implementation, with a negligible
effect on overall results.

>>>>

@@

@@

Dependencies between tasks are determined by a dependence
relation. The
dependence relation identifies the tasks from the
previous time step each task depends on, permitting a wide variety
of patterns to be implemented that are relevant to real
applications: stencils,
sweeps, FFTs, trees, etc. Dependence relations may be
parameterized, such as picking the $K$ nearest neighbors, or $K$
distant neighbors. They may also vary over time, such as in the FFT pattern. The set of dependence relations is extensible, making it easy to add patterns to represent new classes of applications. Table~\ref{tab:equations} shows equations for the
dependence relations of the patterns in Figure~\ref{fig:task-graphs},
where $t$ is timestep, $i$ is column, and $W$ is the width of the task
graph.

@@

The Task Bench core library is fully validating. {\color{blue} The output of each
task is a tuple (time step, column) and is unique within a task
graph. All inputs are verified by checking the expected dependencies
against those received, and an assertion is thrown if validation
fails. These checks ensure that every execution of Task Bench is
correct. Note that the graph representation is concise, making these
checks very inexpensive.} An evaluation of the performance impact of
validation showed it to be less than 3\% at the smallest task
granularities in any Task Bench implementation, with a negligible
effect on overall results.
